Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-06-02 paper/main.tex
minor changes

@@

They studies the alignment of the angular momentum dark relative to
the surrounding large scale structure and to the tidal tensor
eigenvalues.

>>>>

We thank Kristin Riebe for her work to make the cosmic-web data available in the Multidark database.

@@

They study the alignment of the angular momentum dark relative to
the surrounding large scale structure and to the tidal tensor
eigenvalues.
